Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-01-31 paper/paper.tex
Add submission details

\noindent The summary of items from the MODELS reviews.
\begin{compactitem}
  \item Add recent work published after 2018
  \item Add discussion on the limitation of the approach: what attacks can and cannot be covered, can valid messages be rejected, etc.
  \item Expand the role of Briefcase in the case study with input examples to provide more proof of the proposed model's effectiveness on the hardened system (e.g., show a malformed line search task, it's filter, and why it works) 
  \item Clarify research questions answered by the case study and make the figures bigger
  \item Discuss what efforts are optimized with the automations versus a fully manual process for creating the components--how does the automated transformation affect actual time for engineers
  \item Without verifying the correctness of the transformations, can prevention of certain attacks be guaranteed?
\end{compactitem}
\section{Simple Example} \label{sec:example}
\input{example}

>>>>

\noindent The summary of items from the MODELS reviews.
\begin{compactitem}
  \item Add recent work published after 2018
  \item Add discussion on the limitation of the approach: what attacks can and cannot be covered, can valid messages be rejected, etc.
  \item Expand the role of Briefcase in the case study with input examples to provide more proof of the proposed model's effectiveness on the hardened system (e.g., show a malformed line search task, it's filter, and why it works) 
  \item Clarify research questions answered by the case study and make the figures bigger
  \item Discuss what efforts are optimized with the automations versus a fully manual process for creating the components--how does the automated transformation affect actual time for engineers
  \item Without verifying the correctness of the transformations, can prevention of certain attacks be guaranteed?
\end{compactitem}
\noindent Go to \url{https://mc.manuscriptcentral.com/sosym/}. Create a new account (if you don't have one), login and go to the "Author"-section, select the link "Start New Submission" under Author Dashboard and select "Special Section Paper" as the paper type, and choose "MODELS 2021 Special Issue". Also, make sure to mention the MODELS 2021 special issue in the cover letter.

\section{Simple Example} \label{sec:example}
\input{example}
